---
title: "Chicken Feed"
author: "Alexandra Shields-Knox"
date: "03/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

##  Chicken feed study  

data set has chicken weights and 4 variables:
  1.  chicken weight  
  2.  chicken feed type  
  3.  chicken time in the 40" run  
  4.  chicken sex   

Idea is to determine which of the variables affect chicken weight 
The weight and time to run are numerical variables, gender and feed type are categorical variables

So we'll use templatesRMD Cat Numerical, look for the section that has an 'aov'

<!-- This question is like a bunch of t-tests, but instead of doing the t-test a bunch of times we use ANOVA to do all the comparisons at once!  !-->

### get the data

```{r}
chickenData = read.csv('chickens.csv')
head(chickenData)
attach(chickenData)
```

### Graphical summary

<!-- plot chicken weight against each of the three explanatory variables.  Weight against a categorial varable is a boxplot, weight against a numerical variable is a scatter plot !-->

Boxplot of weight based on feed

```{r}
plot(weight~feed,data=chickenData)
```

It appears that type of feed does have an effect on weight. Sunflower appears to be the best because of the lowest variability.





Boxplot of weight based on sex

```{r}
plot(weight~sex,data=chickenData)
```

It appears that male chickens weight slightly more than female chickens on average.



Scatterplot of weight based on speed

```{r}
plot(weight~speed,data=chickenData)
```

Speed does not appear to have any relationship to weight of the chicken.


### Numerical summary

```{r}
summary(chickenData)
```

This is a summary of all of the data in chickenData

### Inference -- Analysis of Variance

```{r}
model1 = lm(weight~feed+speed+sex, data=chickenData)
anova(model1)
```

The variance table shows that only feed affects chicken weight.

###  Conclusions  -- which variables affect chicken weight?

It appears that feed was the only variable that had any effect on chicken weight.

